---
title: "Regression models project"
author: "Kirty Vedula"
date: "04/26/2015"
output: pdf_document
---

## Load libraries
```{r calling_libraries}
library(knitr)
library(markdown)
```
## Loading data from mtcars dataset
``` {r load_data}
data(mtcars)
str(mtcars)
```
## Setting up the variables and levels for Auto and Manual transmission
```{r variables_and_levels}
mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
mtcars$am <- factor(mtcars$am)
levels(mtcars$am) <- c("Auto", "Manual")
```
## Performing Student t-test and Wilcox test
``` {r ttest_and_wilcoxtest}
t.test(mpg ~ am, data = mtcars)
wilcox.test(mpg ~ am, data = mtcars)
```

## Fitting a linear model with the mtcars dataset
```{r model}
model.all <- lm(mpg ~ ., data = mtcars)
model <- step(model.all)
summary(model)
```
## Fitting an ANOVA model
```{r anova_model}
model0 <- lm(mpg ~ am, data = mtcars)
anova(model0, model)
```
## Calculating leverage 
An observation that has an unusual X value—i.e., it is far from the mean of X—has leverage on (i.e., the potential to influence) the regression line 
```{r leverage}
leverage <- hatvalues(model)
leverage[which(leverage > 0.5)]
```

## Calculating influential
Only when an observation has high leverage and is an outlier in terms of Y-value will it strongly influence the regression line
```{r influential}
influential <- dfbetas(model)
influential[which(abs(influential) > 1)]
```
## Quantifying the MPG difference between automatic and manual transmissions
``` {r plot_mpg_am}
plot(mpg ~ am, data = mtcars, main = "Mpg by transmission type", xlab = "Transmission type", ylab = "Miles per gallon")
pairs(mtcars, panel = panel.smooth, main = "Pairs graph for MTCars")
par(mfrow = c(2, 2))
plot(model)
```
